strucplots---Visualizing higher-dimensional Contingency Tables in \pkg{vcd}

### 2005-08-01 trunk/vcd/inst/doc/strucplot.Rnw
plots enhanced
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@419 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[h]
\begin{center}
<<Variables,fig=TRUE,echo=FALSE,height=6,width=16,results=hide>>=
pushViewport(viewport(layout = grid.layout(ncol = 2)))

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[h]
\begin{center}
<<cotabplot,fig=TRUE,echo=FALSE,height=6,width=12,results=hide>>=
cotabplot(~ Class + Survived | Sex + Age, data = Titanic)
@
\caption{cotabplot for the Titanic data.}
\label{fig:cotabplot}
\end{center}
\end{figure}

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[h]
\begin{center}
<<afterplot,fig=TRUE,echo=FALSE,height=6,width=12,results=hide>>=
mosaic(~ Sex + Class, data = Titanic, pop = FALSE)

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[h]
\begin{center}
<<changeplot,fig=TRUE,echo=FALSE,height=6,width=12,results=hide>>=
assoc(Titanic)
getNames() ## output not shown
grid.edit("rect..Class.1st..Age.Adult..Sex.Female..Survived.Yes", 
          gp = gpar(fill = "red"))
@
\caption{Changing graphical parameters of elements after drawing.}
\label{fig:changeplot}
\end{center}
\end{figure}

>>>>

\setkeys{Gin}{width=\textwidth}
\begin{figure}[h]
\begin{center}
<<Variables,fig=TRUE,echo=FALSE,height=6,width=16,results=hide>>=
pushViewport(viewport(layout = grid.layout(ncol = 2)))

@@

\setkeys{Gin}{width=\textwidth}
\begin{figure}[h]
\begin{center}
<<cotabplot,fig=TRUE,echo=FALSE,height=6,width=12,results=hide>>=
cotabplot(~ Class + Survived | Sex + Age, data = Titanic)
@
\caption{cotabplot for the Titanic data.}
\label{fig:cotabplot}
\end{center}
\end{figure}

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[h]
\begin{center}
<<afterplot,fig=TRUE,echo=FALSE,height=6,width=6,results=hide>>=
mosaic(~ Sex + Class, data = Titanic, pop = FALSE)

@@

\setkeys{Gin}{width=0.7\textwidth}
\begin{figure}[h]
\begin{center}
<<changeplot,fig=TRUE,echo=FALSE,height=6,width=6,results=hide>>=
assoc(Titanic)
x = Titanic
x[] = NA
x["1st", "Female", "Adult", "Yes"] = "Red"
assoc(Titanic, gp = gpar(fill = x))
@
\caption{Changing graphical parameters of elements after drawing.}
\label{fig:changeplot}
\end{center}
\end{figure}
